**Preprinting Microbiology**

### 2017-03-13 submission/Schloss_PrePrints_mBio_2017.Rmd
Add evolving analysis Zika preprint
Not only can preprints be updated with multiple versions, but
some people are using them to slowly roll out late breaking
data collection and analyses in the hope of reducing the friction
of studying a novel area. Closes #9

First, preprints have proven useful for rapidly disseminating results for disease outbreaks and new technologies. Prior to the recent Zika virus outbreak there were approximately 50 publications that touched on the biology and epidemiology of the virus; as of January 2017 the number of Zika virus-related publications was over 1,700. During the recent outbreak, more than 110 Zika virus-related preprints have been posted at *bioRxiv*. Any manuscript that was published went through several month delays in releasing information to health care workers, the public, and scientists needing to learn new methods to study a previously obscure virus. In contrast, those that posted their work as a preprint were able to disseminate their methods and results instantly. Over the last several years there have also been rapid advances in DNA sequencing technologies that have fundamentally changed how microbial science is performed. One notable technology, the MinIon sequencing platform from Oxford Nanopore, has received considerable attention from researchers who have posted more than 90 preprints describing new MinIon-based methods and results to preprint servers. For such a rapidly developing technology, the ability to share and consume methods from other scientists has created a feed forward effect where the technology has likely advanced at a faster rate than it otherwise would have.

@@

I am grateful to Stefano Bertuzzi and Lynn Enquist for their helpful comments on earlier versions of this manuscript and to the numerous individuals who provided feedback on the preprint version of the manuscript. This work was supported in part by funding to PDS from the National Institutes of Health (P30DK034933). I appreciate the support of Altmetric, Inc and Thompson Reuters who provided advanced programming interface (API) access to their databases. The workflow utilized commands in GNU make (v.3.81), GNU bash (v.4.1.2), and R (v.`r paste(version$major, version$minor, sep='.')`). Within R I utilized the cowplot (v.`r packageDescription("cowplot")$Version`), dplyr (v.`r packageDescription("dplyr")$Version`),
ggplot2 (v.`r packageDescription("ggplot2")$Version`), httr (v.`r packageDescription("httr")$Version`), RCurl (v.`r packageDescription("RCurl")$Version`),
rentrez (v.`r packageDescription("rentrez")$Version`), rjson (v.`r packageDescription("rjson")$Version`), rvest (v.`r packageDescription("rvest")$Version`), sportcolors (v.`r packageDescription("sportcolors")$Version`), and tidyr (v.`r packageDescription("tidyr")$Version`) packages. A reproducible version of this manuscript and analysis is available at http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017.

>>>>

First, preprints have proven useful for rapidly disseminating results for disease outbreaks and new technologies. Prior to the recent Zika virus outbreak there were approximately 50 publications that touched on the biology and epidemiology of the virus; as of January 2017 the number of Zika virus-related publications was over 1,700. During the recent outbreak, more than 110 Zika virus-related preprints have been posted at *bioRxiv*. Any manuscript that was published went through several month delays in releasing information to health care workers, the public, and scientists needing to learn new methods to study a previously obscure virus. In contrast, those that posted their work as a preprint were able to disseminate their methods and results instantly. Another interesting use of preprints to disseminate new information about Zika virus has been the posting of a preprint describing the Zika virus outbreak in the US Virgin Islands that will be continually updated as new data and analyses are performed [@Black2017]. Over the last several years there have also been rapid advances in DNA sequencing technologies that have fundamentally changed how microbial science is performed. One notable technology, the MinIon sequencing platform from Oxford Nanopore, has received considerable attention from researchers who have posted more than 90 preprints describing new MinIon-based methods and results to preprint servers. For such a rapidly developing technology, the ability to share and consume methods from other scientists has created a feed forward effect where the technology has likely advanced at a faster rate than it otherwise would have.

@@

I am grateful to Stefano Bertuzzi and Lynn Enquist for their helpful comments on earlier versions of this manuscript and to the numerous individuals who provided feedback on the preprint version of the manuscript. This work was supported in part by funding from the National Institutes of Health (P30DK034933). I appreciate the support of Altmetric, Inc and Thompson Reuters who provided advanced programming interface (API) access to their databases. The workflow utilized commands in GNU make (v.3.81), GNU bash (v.4.1.2), and R (v.`r paste(version$major, version$minor, sep='.')`). Within R I utilized the cowplot (v.`r packageDescription("cowplot")$Version`), dplyr (v.`r packageDescription("dplyr")$Version`),
ggplot2 (v.`r packageDescription("ggplot2")$Version`), httr (v.`r packageDescription("httr")$Version`), RCurl (v.`r packageDescription("RCurl")$Version`),
rentrez (v.`r packageDescription("rentrez")$Version`), rjson (v.`r packageDescription("rjson")$Version`), rvest (v.`r packageDescription("rvest")$Version`), sportcolors (v.`r packageDescription("sportcolors")$Version`), and tidyr (v.`r packageDescription("tidyr")$Version`) packages. A reproducible version of this manuscript and analysis is available at http://www.github.com/SchlossLab/Schloss_PrePrints_mBio_2017.
